### 2023-08-15 README.Rmd
Update README.Rmd

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.pdf`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/data/): Data output from `data-raw/*.R`, used in the analysis (*.rda*).
  - [:file\_folder: analysis/figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: R](/R/): R functions.
  - [:file\_folder: data-raw](/data-raw/): R script to download and process the raw data from Zenodo (https://zenodo.org/record/8061483).

@@

This research compendium has been developed using the statistical programming
language R. To work with the compendium, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself and optionally [RStudio Desktop](https://rstudio.com/products/rstudio/download/).

>>>>

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis.
  - [:file\_folder: data](/data/): Data output from `data-raw/*.R`, used in the analysis (*.rda*).
  - [:file\_folder: analysis/figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.
  - [:file\_folder: R](/R/): R functions required in the analysis.
  - [:file\_folder: data-raw](/data-raw/): R script to download and process the raw data from Zenodo (https://zenodo.org/record/8061483).

@@

This research compendium has been developed using the statistical programming
language R. To work with the compendium, you will need
installed on your computer the [R software](https://cloud.r-project.org/)
itself, optionally (but recommended) [RStudio Desktop](https://rstudio.com/products/rstudio/download/), and [Quarto](https://quarto.org/docs/get-started/).
